A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-23 doc/paper1-submission/paper5.tex
Add section about output tree accuracy.

>>>>

Our supertree pipeline makes it possible to summarize and merge
information from across the tree of life.  However, we do not claim
that our supertree is more accurate than the input trees that is
summarizes.  We demonstrate that ranks supplied by curators have
substantial effects on the output of the pipeline.  Currently every
node in an input tree must recieve the same rank, and bootstrap
proportions and posterior probabilities are not taken into account.
Therefore, before using the output of our supertree pipeiline in an
evolutionary analysis, researchers must first assess the accuracy of
the output supertree, possibly adjusting the ranks of the input trees
to produce a more useful outcome.
